---
title: "Lab 6 Comparing two means"
author: "Lara Al Selim"
date: "04.29.2021"
output: github_document
---

Researchers studying the number of electric fish species living in various parts of the Amazon basin were interested in whether the presence of tributaries affected the local number of electric fish species in the main rivers (Fernandes et al. 2004).

They counted the number of electric fish species above and below the entrance point of a major tributary at 12 different river locations.

The data is provided in your GitHub repository.

For each question below, write a sentence answering the question and show the code you used to come up with the answer, if applicable.

```{r}
library(tidyverse)
fish <- read_csv("chap12q19ElectricFish.csv")
fish_long <- 
  pivot_longer(fish, speciesUpstream:speciesDownstream,
               names_to = "location",
               values_to = "species") %>% 
  mutate(location = str_remove(location, c("species"))) %>% 
  print()
```

## Question A

> Test the hypothesis that the tributaries have no effect on the number of species of electric fish.

```{r t-test}
fish_ttest <- t.test(species ~ location, data = fish_long)
diff(fish_ttest$estimate)
```

ANSWER
The Null hypothesis is that the tributaries have no effect on the number of species of electric fish, and the Alternate hypothesis is that the tributaries do have an effect on the number of species of electric fish.

## Question B

> What is the difference in the mean numbers of species between areas upstream and downstream of a tributary? What is the 95% confidence interval of this difference in means?

ANSWER
The difference in the mean numbers of species between areas upstream and downstream of a tributary is -1.83 and the true difference in means is between 
-4.59 and 8.25.

## Question C

> State the assumptions that you had to make to complete parts (A) and (B). Create a graph to assess whether one of those assumptions was met.

ANSWER
The assumption was that the tributaries had no effect on the number of species of electric fish.

```{r}
fish_long %>% 
  ggplot(aes(x = location, y = tributary)) +
  geom_jitter(aes(color = location), 
  shape = 16, alpha = 0.9, width = 0.9) 
```
